\LARGE \bf Expectation-Maximization based defense mechanism for distributed Model Predictive Control

### 2022-01-31 article/article.tex
add challenge and time dependency

\todo{As seen in~\cite{BemporadEtAl2002,BorrelliEtAl2017}, the solution for a constrained linear quadratic regulation problem yields in a \pwa{} function.
Similarly, we can get an explicit  solution for its dual variables $\vec{\lambda}_{i}$, which is also a \pwa{} function with respect to $\vec{\theta}_{i}$:}
\begin{equation}
  \begin{aligned}
    \label{eq:lambdafuntheta}
    \lambdai=
    \begin{cases}
      -P_{i}^{1}\vec{\theta}_{i}-\vec{s}_{i}^{1}[k]&\text{if}\ G_{1}\thetai \preceq z_{1} \\
      \qquad\quad \vdots&\qquad\quad \vdots\\
      -P_{i}^{N}\vec{\theta}_{i}-\vec{s}_{i}^{N}[k]&\text{if}\ G_{N}\thetai \preceq z_{N} \\
    \end{cases}
  \end{aligned}
\end{equation}
The halfspaces defined by the set of pairs $(G_{j},z_{j})$ represent a combination of active constraints.
As each constraint can be active or inactive, for a group of $n$ constraints, \todo{potentially} we can have $N=2^{n}$ different combinations of active/inactive sets, consequently $N$ regions (or zones).
\todo{
  Here we say potentially because depending on the constraints, some of these combinations can be infeasible.\question{Remove??}
}

>>>>

\todo{As seen in~\cite{BemporadEtAl2002,BorrelliEtAl2017}, the solution for a constrained linear quadratic regulation problem yields in a \pwa{} function.
Similarly, we can get an explicit  solution for its dual variables $\vec{\lambda}_{i}$, which is also a \pwa{} function with respect to $\vec{\theta}_{i}$:}
\begin{equation}
  \begin{aligned}
    \label{eq:lambdafuntheta}
    \lambdai=
    \begin{cases}
      -P_{i}^{1}\vec{\theta}_{i}-\vec{s}_{i}^{1}[k]&\text{if}\ G_{1}[k]\thetai \preceq z_{1}[k] \\
      \qquad\quad \vdots&\qquad\quad \vdots\\
      -P_{i}^{N}\vec{\theta}_{i}-\vec{s}_{i}^{N}[k]&\text{if}\ G_{N}[k]\thetai \preceq z_{N}[k] \\
    \end{cases}
  \end{aligned}
\end{equation}
The halfspaces defined by the set of pairs $(G_{j}[k],z_{j}[k])$ represent a combination of active constraints for a given time $k$.

\begin{challenge}
It is important to note that since the actual state is unknown we cannot anticipate how the space is partitioned, nor the values of $\vec{s}_{i}[k]$.
\end{challenge}
 As each constraint can be active or inactive, for a group of $n$ constraints, \todo{potentially} we can have $N=2^{n}$ different combinations of active/inactive sets, consequently $N$ regions (or zones).
\todo{
  Here we say potentially because depending on the constraints, some of these combinations can be infeasible.\question{Remove??}
}
